Paper 1

### 2022-05-26 scripts/Paper 1.Rmd
update

#below is precip data from liaweenee - it only goes up to Jan 2022 right now
rainfall_L <- read.csv("R:/SET/PlantSci/Shared Work Spaces/Ecology/Peoples files/Marion Nyberg/PhD/Rainfall/rainfall.csv")
rainfall_L <- rainfall_L[-1]
colnames(rainfall_L)[4] <- "Precip"
rainfall_L$Year <- as.factor(rainfall_L$Year)

@@

@@

Total monthly precipitation at Silver Plains. The BOM average is data from the Interlaken Estate (1995-2021), however, there are multiple missing values, so results may be underestimated.

@@

```{r Air temperature, echo=FALSE, message = FALSE, fig.width = 10, fig.height = 4}
ggplotly(ggplot(input.daily, aes(x = jday, y = Ts, group = Year)) +
  geom_line(aes(color = Year))+
  theme_classic())

>>>>

#below is precip data from liaweenee - it only goes up to Jan 2022 right now
rainfall_L <- read.csv("R:/SET/PlantSci/Shared Work Spaces/Ecology/Peoples files/Marion Nyberg/PhD/Rainfall/rainfall.csv")
rainfall_L <- rainfall_L[-1]
colnames(rainfall_L)[4] <- "Precip"
rainfall_L$Year <- as.factor(rainfall_L$Year)
rainfall_L <- rainfall_L %>% filter(Year == 2019)
colnames(rainfall_L)[3] <- "jday"
colnames(rainfall_L)[2] <- "month"
rainfall_L$Site <- "L"

@@

rainfall.SP <- input.daily %>% select(Precip, jday, month, Year)
rainfall.SP$Site <- "SP"

rainfall <- rbind(rainfall_L, rainfall.SP)

@@

@@

```{r Air temperature, echo=FALSE, message = FALSE, fig.width = 10, fig.height = 4}
